---
title: "MD5"
format: html
editor: visual
embed-resources: true
---

```{r}
library(tidyverse)
library(moderndive)
library(skimr)
library(gapminder)
```

```{r}
#| message: false
library(tidyverse)

twitch_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/twitchdata-update.csv")
```

```{r}
#| message: false
library(janitor)
twitch_data <- clean_names(twitch_data)

# Inspect new names
colnames(twitch_data)
```

```{r}
twitch_data %>% 
sample_n(size = 5)
```

Q.1 Part a)

Q:Describe the results in a few words. Does anything capture your attention?

A:They all have very large watch time minutes but some have very low average viewers.

```{r}
twitch_data %>% 
  select(average_viewers, followers) %>% 
  summary()
```

Q.1 Part b)

Q:Does anything capture your attention?

A: The amount of followers doesn't equal amount of average viewers.

```{r}
ggplot(twitch_data,
aes(x = average_viewers,
    y = followers)) +
  geom_jitter(alpha = .3)
```

Q.1 Part c)

Q: What do you notice? (scatterplot)

A: The points are very clustered at the bottom left.

```{r}
ggplot(twitch_data,
aes(x = average_viewers,
    y = followers)) +
  geom_jitter(alpha = .3) +
 scale_x_log10() +
  scale_y_log10()
```

Q.1 Part d)

Q: What do you see now? How does the relationship look like?

A: They are a lot more open and up to scale and it looks like a positive relationship.

```{r}
twitch_data <- twitch_data %>% 
  mutate(log_viewers = log10(average_viewers), 
         log_followers = log10(followers))
```

Q.2)

```{r}
fit1 <- lm(log_viewers ~ log_followers, data = twitch_data)
get_regression_table(fit1)
```

Issue with rendering. Code chunk below

{r}

tidy(fit1)

Q.2 Part a)

Q:Take the coefficient from your model and interpret it in this way.

Equation: \$\$ 1.1\^(.588) = 1.057

A: A 10% increase in followers is associated with a 5.7% increase in the average number of viewers

Q.3)

```{r}
library(broom)

pred_data <- augment(fit1)

# glimpse our new data 
glimpse(pred_data)
```

```{r}
pred_data %>% 
  ggplot(aes(x = log_followers, 
             y = log_viewers)) +
  geom_jitter(alpha = 0.4) + 
  geom_line(aes(x = log_followers, 
                y = .fitted), 
            col = "orange") + 
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

Q.3 Part A)

Q:Do you think our model describes the relationship well?

A: Yes, it goes through the majority of the function.

Q.3 Part B)

```{r}
pred_data %>% 
  ggplot(aes(x = log_followers, 
             y = .resid)) +
  geom_jitter(alpha = 0.4) + 
  geom_smooth(method = lm) + 
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

Q: What do you see? Are there any big residuals? DO they happen often in a particular range of our x-variable? If so, we would have a problem: our model would systematically fail to predict part of our data.

A: There are some residuals off of the line but its normal going through the plot. They are often but they are mostly close to the line of best fit.

Q.4)

```{r}
fit2 <- lm(log_viewers ~ language, data = twitch_data)
get_regression_table(fit2)
```

```{r}
tidy(fit2)
```

```{r}
q_four <- augment(fit2)
```

```{r}
q_four %>% 
  ggplot(aes(x = log_viewers, 
             y = language)) + 
  geom_boxplot() +
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

Q.5)

```{r}
twitch_data <- twitch_data %>% 
  mutate(language = as.factor(language), 
         language = relevel(language, ref = "English"))
```

```{r}
twitch_data %>% 
  ggplot(aes(x = log_viewers, 
             y = language)) +
  geom_jitter() + 
  geom_line(aes(x = log_viewers, 
                y = "English"), 
            col = "orange") +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "Average viewers", 
       y = "Languages")
```

Q:Interpret the results. How is my prediction doing?

A: English is one of the highest means other than Spanish but it odes have quite a few outliers that have a lot of more viewers helping the prediction.

Q.6)

```{r}
q_four %>% 
  ggplot(aes(x = log_viewers, 
             y = .resid)) +
  geom_smooth(method = lm) + 
  geom_jitter(alpha = .2) +
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

Q:There are a couple of points our model really missed - which ones were they?

A: The ones on the bottom left there seems to be a lot more than other grpahs shown.
