---
title: "MD7"
format: html
editor: visual
embed-resources: true
---

```{r}
#| message: false
library(tidyverse)
library(here)
library(moderndive)
library(readr)
library(tibble)
```

```{r}
#| message: false
library(readr)
nobel_winners <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/nobel_winners.csv")
```

```{r}
nobel_winners_flt <- nobel_winners %>% 
  filter(category != "Peace") %>% 
  mutate(is_us = if_else(birth_country == "United States of America", 1, 0))
```

```{r}
true_prop <- nobel_winners_flt %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))

ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  labs(x = "Proportion")
```

```{r}
set.seed(33)
# Random sample 
our_sample <- sample_n(nobel_winners_flt, 
                       size = 25, 
                       replace = F)

sample_prop <- our_sample %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(our_sample))

# How does our proportion look like? 
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  geom_vline(xintercept = sample_prop[2,2][[1]], linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

Q.1)

Q: In this scenario, what is the population?

-   What is the sampling frame?

-   A: Nobel prize winners in science then in the US

-   What does the black line represent? (hint: the word population is in the name).

-   A: The true proportion

-   What does the red line represent?

-   A: The random sample proportion of us born Nobel prize winners in a sample of 25 excluding women

Q.2)

```{r}
nobel_25 <- nobel_winners_flt %>% 
  rep_sample_n(size = 25, reps = 50) %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(is_us)/25)
```

```{r}
ggplot(nobel_25,
      aes(x = prop)) +
  geom_histogram(binwidth = .02) +
  geom_vline(aes(xintercept = mean(prop)))
```

Q.3)

```{r}
nobel_100 <- nobel_winners_flt %>% 
  rep_sample_n(size = 100, reps = 50) %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(is_us)/100)
```

```{r}
ggplot(nobel_100,
      aes(x = prop)) +
  geom_histogram(binwidth = .0052) +
  geom_vline(aes(xintercept = mean(prop)))
```

Q.4)

```{r}
sd_nobel_25 <- nobel_winners_flt %>% 
  rep_sample_n(size = 25, reps = 50) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))
```

```{r}
sd_nobel_100 <- nobel_winners_flt %>% 
  rep_sample_n(size = 100, reps = 50) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))
```

```{r}
sd_nobel_25 %>% 
  summarise(sd = sd(prop))
```

```{r}
sd_nobel_100 %>% 
  summarise(sd = sd(prop))
```

Q: Do these results support your argument above? What does this imply about sample size? What happens to the variability in our estimates as the sample size increases

A: No this doesn't support the argument as it says there isnt and devation while there is. The sample size does increase proprtion but the variability stays the same.

Q.5)

```{r}
nobel_winners_flt <- nobel_winners_flt %>% 
  mutate(gender1 = if_else(gender == "Female", 1,0))
```

```{r}
female_nobel <- nobel_winners_flt %>% 
  rep_sample_n(size = 100, reps = 50) %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(gender1)/50)
```

```{r}
ggplot(female_nobel,
      aes(x = prop)) +
  geom_histogram(binwidth = .01) +
  geom_vline(aes(xintercept = mean(prop)))
```

Q.6)

Q: Explain the **Central Limit Theorem** it in your own words. Be as concise as you can (i.e., use no more than 3-4 sentences) but convince me you really understand the basic idea.

A: As the size increases, the bell shape and the spread of the distribution decreases. This allows the distribution to continue and get close to the tru distribution proportion. The normality of a distribution is in accordance to the sample size. This normality is shown with a tall peak above the rest of the sample size.
