---
title: "My homework"
format: html
editor: visual
embed-resources: true
---

Q.1)

```{r}
#| message: false
library(tidyverse)
# Read in the data 
exercise_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/visualize_data.csv")
glimpse(exercise_data)
```

Correlation is connected but probably a p-value of .5

```{r}
cor(exercise_data$Exercise, exercise_data$BMI)
```

```{r}
ggplot(data = exercise_data,
   aes(x = Exercise,
       y = BMI)) +
    geom_point()
```

\
Q.2)

Q:"Before we move forward, we want to know what these variables capture. Run `?corruptDF` and tell me in your own words what `CPI2017` and `HDI2017` capture."

A: Information on a variety of countries explaining each of their Human development index and Corruption perception index in the year 2017.

```{r}
#| message: false
library(causact)
glimpse(corruptDF)
```

```{r}
#| message: false
?corruptDF
```

Q.3

Q: Describe the relationship that you see

A: Positive correlational relationship meaning as HDI increases, CPI increases.

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017)) +
  geom_point()

```

Q.4

Q:What are the differences? Which one do you prefer?

A:The differences is that lm shows the correlation of the P-value. While gam shows the line of formation around the the data points.

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017)) +
  geom_point() +
  geom_smooth(method = "gam")
```

Q.5

Q:What do you see? Are patterns clear or is the graph too cluttered? What would be another way to get these trends by region but in a way to would be more legible?

A:They were really clustered but it wasn't able to show the separation of regions but the facet wrap of regions separated them and made them look a lot more legible.

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017,
           color = region,
           fill = region)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap("region")
```

Q.6

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017,
           color = region,
           fill = region)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap("region") +
  scale_x_reverse()
```

Q.7

```{r}
ggplot(data = corruptDF,
       aes(x = HDI2017,
           y = CPI2017,
           color = region,
           fill = region)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap("region") +
  labs(x = "Human Development Index",
       y = "Corruption Development Index",
       title = "Correlation between HDI and CPI by Reigon In 2017",
       subtitle = "Sources from Corrup DF")
```

Q.8

```{r}
ggsave("HDI_CDI_plot.png")
```
